\section{Experience}
\cventry[1em]{2019--Current}{Software Development Engineer}{Amazon Lab 126}{Sunnyvale}{}
{Experienced software engineer leveraging my expertise in large-scale \textit{distributed system design}, \textit{cloud technologies} 
and \textit{data-driven development} to build highly available, scalable \textit{microservices} with 
\textit{AWS} on \textit{Java}, \textit{Python} frameworks for cross-team initiatives.\newline{}
\begin{itemize}
\setlength\itemsep{1em}
    \item Rearchitected the Target Recommendation Service
        \begin{itemize}
            \item Spearheaded the re-architecture of a critical service using \textit{structural and behavioral design patterns} for enhanced efficiency and maintainability.
            \item Implemented core product components, enabling the use of business metrics to support \textit{data-driven} decision making.
            \item Demonstrated expertise in system design, scalability, and the development of metrics-driven solutions.
        \end{itemize}
    \item Space based targeting for 3P Smart-home Devices
    \begin{itemize}
        \item Designed and implemented a scalable rule engine to optimize smart-home device targeting.
        \item Reduced operational \textit{costs by 50\%} through service call optimization, demonstrating resourcefulness and focus on efficiency.
        \item Demonstrated \textit{strong problem-solving skills} in a complex, data-driven environment.
    \end{itemize}
    \item Launch Vega Family of Devices
        \begin{itemize}
            \item Collaborated with cross-functional teams (device software, video, middleware) to launch new OS -- Vega for media playback.
            \item Designed solutions that \textit{mitigated latency degradation} and \textit{reduced scaling costs}, demonstrating focus on \textit{performance and cost optimization}.
            \item Showcased the ability to work \textit{effectively across teams} to deliver a complex product launch.
        \end{itemize}
    \item LLM Prompt Engineering for Alexa Endpoint Context Service
        \begin{itemize}
            \item Engineered a system to enhance LLM (\textit{Large Language Model}) action generation using Langchain, minimizing the need for extensive fine-tuning.
            \item Developed a \textit{few-shot prototype} to improve context handling, resulting in increased LLM robustness.
            \item Successfully integrated multiple service with LLMs by chaining APIs together.
        \end{itemize}
\end{itemize}}

\cventry[1em]{2015--2019}{Software Development Engineer}{Amazon Development Centre India}{Bengaluru}{}
{Led development and management of Seller onboarding microservices for Amazon.in launch.\newline{}
\begin{itemize}
\setlength\itemsep{1em}
    \item Launch of Out of Country Merchants in India 
        \begin{itemize}
            \item Designed international merchant registration pipeline, accelerating India market expansion.
            \item Enhanced multiple customer touchpoints with precomputation and caching, reducing latency.
        \end{itemize}
    \item AWB and Commercial Invoice Generation
        \begin{itemize}
            \item Built invoice generation service, integrating \textit{AWS SQS} for real-time order processing.
            \item Streamlined audit workflows with automated SFTP invoice transfer to Deutsche Bank.
            \item Ensured compliance and streamlined financial processes with secure invoice generation.
        \end{itemize}
\end{itemize}}